Balance responses in MS

### 2020-01-17 R/msBalance.Rmd
updated table and figure captions

## Data sources
This study performed a secondary analysis on existing electromyographic recordings during balance responses in people with and without MS.
Inclusion criteria for MS participants were as follows: diagnosis of MS by a MS neurologist and no relapses within 60 days.
Inclusion criteria for all participants included ability to walk 25 ft (7.6 m) without an assistive device, and no other known biomechanical or neurologic conditions affecting stepping or balance.
Clinical and demographic characteristics of the study sample are summarized in Table 1.

@@

```{r layout}
library(captioner)
tableNumbers <- captioner(prefix = "Table")
captionDemographics = tableNumbers(name = "demographics", caption = "Clinical and demographic features of the study population.")
figureNumbers <- captioner(prefix = "Figure")
captionCartoon = figureNumbers(name = "cartoon", caption = "Perturbation directions used in testing protocol.")
```

@@

```{r perturbationFigure, out.width = "25%", fig.align = "center", fig.cap = captionCartoon}
knitr::include_graphics("figures/Perturbations.svg")
```

@@

```{r table1}
library(janitor)
library(kableExtra)
participants %>% tabyl(Sex, Group) %>% mutate(Total = MS + Control) %>% 
  kable() %>% kable_styling(full_width = F, position = "left")
```

>>>>

@@

```{r layout}
# layout tables and figures
library(captioner)
tableNumbers <- captioner(prefix = "Table")
captionDemographics = tableNumbers(name = "demographics", caption = "Clinical and demographic features of the study population.")
figureNumbers <- captioner(prefix = "Figure")
captionCartoon = figureNumbers(name = "cartoon", caption = "Perturbation directions used in testing protocol.")
```

## Data sources
This study analyzed existing electromyographic recordings during balance responses in people with and without MS.
An earlier analysis of a subset of these records is available.[@peterson2016]
Inclusion criteria for MS participants were as follows: diagnosis of MS by a MS neurologist and no relapses within 60 days.
Inclusion criteria for all participants included ability to walk 25 ft (7.6 m) without an assistive device, and no other known biomechanical or neurologic conditions affecting stepping or balance.
Clinical and demographic characteristics of the study sample are summarized in `r tableNumbers("demographics", display = "cite")`.

```{r demographics}
library(janitor)
library(kableExtra)
participants %>% tabyl(Sex, Group) %>% mutate(Total = MS + Control) %>% 
  kable(caption = captionDemographics) %>% kable_styling(full_width = F, position = "left")
```

@@

```{r perturbationFigure, out.width = "25%", fig.align = "left", fig.cap = captionCartoon}
knitr::include_graphics("figures/Perturbations.svg")
```

@@
